An observational study of papers published in _PLOS ONE_ and studies posted to a trial registry.

### 2021-04-21 manuscript/asa_template/asa_template.Rmd
update r scripts for boilerplate text

ftab = flextable(ftab.cosine.plos) %>% theme_box() %>% autofit()
ftab <- set_caption(ftab, "Summary of cosine similarity scores by topic: PLOS ONE")
ftab

>>>>

ftab = flextable(ftab.cosine.plos) %>% theme_box() %>% autofit()
ftab <- set_caption(ftab, "Summary of cosine similarity scores among top 500 DOIs assigned to each topic: PLOS ONE")
ftab
